Viscous Transport in Eroding Porous Media

### 2019-05-13 docs/transport/erosion_transport.tex
do the result section of transport paper

The snapshots of the process of 20 nearly touching bodies eroding are in Fig.~\ref{fig:Eroding20vort}. 
We place some bodies to nearly contact not only one another but also the outer boundary. For example, bodies 1, 6, 13, and 15 are very close to outer boundary. In~\cite{qua-moo2018} we reported the quick expanding space at the narrow channel between neighboring bodies, the developing flat faces at the sites of near contact, and bodies vanishing. In this nearly touching bodies structure, we also observe these phenomena but with more new details.
For the speed of expanding space at the narrow channel, we see some narrow channels do expand faster than other wider channels. For example, the spacing between bodies 14 \& 18 is smaller than the spacing between bodies
 7 \& 14 initially and the former one is comparable to the latter one by the second frame. But there are some small initial spacings that do not expand that much at all by the fourth frame, for example between bodies 1 \& 6, 3 \& 9. 
We could find the explanation from the trajectories of tracers in Fig.~\ref{fig:Eroding20tracer}. Since the direction of flow is from left to right, most of the tracers will not travel vertically but horizontally when the gaps or channels are too small.  }

>>>>

The snapshots of the process of 20 nearly touching bodies 
eroding are in Fig.~\ref{fig:Eroding20vort}. 
We place some bodies to nearly contact not only one another 
but also the outer boundary. For example, bodies 1, 6, 13, and 15 
are very close to outer boundary. In~\cite{qua-moo2018} 
we reported the quick expanding space at the narrow channel 
between neighboring bodies, the developing flat faces at the sites 
of near contact, and bodies vanishing. In this nearly touching bodies 
structure, we also observe these phenomena but with more new details.

For the speed of expanding space at the narrow channel, we see some 
narrow channels do expand faster than other wider channels. 
For example, the spacing between bodies 14 \& 18 is smaller 
than the spacing between bodies 7 \& 14 initially and the former one is 
comparable to the latter one by the second frame. But there are some 
small initial spacings that do not expand that much at all by the fourth frame, 
for example between bodies 1 \& 6, 3 \& 9. 
We could find the explanation from the vorticity of fluid 
in Fig.~\ref{fig:Eroding20vort}. 
Since the eroding velocity on the body is proportional to the 
absolute value of vorticity in our erosion model,  
then when the  absolute value of vorticity is small 
there is not much erosion on the body. 
In all four frames of Fig.~\ref{fig:Eroding20vort}, 
the vorticity is relatively small between bodies 1 \& 6 and 3 \& 9.

Since the direction of flow is from left to right, most of the tracers will not travel vertically but horizontally when the gaps or channels are too small.  }
